The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-21 paper.tex
update

  A crucial ingredient in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$ in real space,\
  and the power-law Kolmogorov spectrum
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has the cutoff wave number $k_{\text{min}}=375.0$,\
  corresponding to the average clump sizes of $\sim 20$ pc.

>>>>

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.
  The spatial density distribution $\rho(\bold{x})$ of clumpy ISM obeys\
  the log-normal probability distribution \citep{Berkhuijsen2008} with mean $\mu=1.3$ and dispersion $\sigma=0.13$,\
  and the power-law Kolmogorov spectrum
  \begin{equation}
    D(k)=\int k^{2} \hat{\rho}(k)\hat{\rho}^{*}(k)dk \propto k^{-5/3},
  \end{equation}
  where $\hat{\rho}(k)$ is the Fourier transform of $\rho(\bold{x})$.\
  The spectrum $D(k)$ with index $-5/3$ in the Fourier space has a cutoff wave number $k_{\text{min}}=375.0$,\
  corresponding to the average clump sizes of $\sim 20$ pc.
